---
title: "Fquality_CJFAS"
author: "Lauren Yamane"
date: "6/28/2019"
output: html_document
---
---
title: "Fquality"
author: "Lauren Yamane"
date: "8/18/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyr)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(readxl)
library(cowplot)
library(colorspace)
```
Measures of F estimate quality from the SSIPM:  inaccuracy (absolute value of mean value for the 10 fits minus the true value of F.  #Old: note that for inaccuracy, the F=0 estimates were left raw rather than transformed with the above equation)  

```{r fquality}
Fstd_all <- read_excel("/R_stuff/R_Research/MPAs/Fstd_all.xlsx")
Fstd_all$species  <- with(Fstd_all, reorder(species, M))

#For case where bias is not calculated as an absolute value
#pal <- choose_palette()
#pal(17)
Fest_noabs<- read_excel("/R_stuff/R_Research/MPAs/Fest_noabs.xlsx")
Fest_noabs$species <- with(Fest_noabs, reorder(species, M))
Fest_noabs <- Fest_noabs 
  
Fest_noabsgg <- ggplot(data = Fest_noabs, aes(F_values, F_est, color = species))
Fest_noabsgg <- Fest_noabsgg + 
  geom_line() + 
  labs(x=expression(paste("True fishing mortality rate (", y^-1, ")")), y="Bias") + theme(legend.title=element_blank()) +
  geom_hline(aes(yintercept=0), linetype = "dashed") +
  stat_summary(fun.y = "mean", colour = "black", size = 1.3, geom = "line") +
  scale_color_manual(values = pal(17))

# To make a plot with F estimate for the true value of F=0.1 on the y-axis
Fest_noabs_true <- read_excel("/R_stuff/R_Research/MPAs/Fest_noabs_2018JAN10.xlsx") ### continued below (see Combined)
```

```{r concatenated_data}
mean_stats <- select(Fest_noabs, -k_M_F) %>% group_by(species) %>% summarise_all(., funs(mean, sd))

sd_stats <- select(Fstd_all, -k_M_F) %>% group_by(species) 
```
These calculations are for the no absolute value analyses, in particular for analyses focused on F = 0.1 only, including theta.  Theta is the angle between the current population vector (in the MPA case, an SAD that is truncated by fishing), and the future SAD population vector (in the MPA case, for the unfished SAD).  See theta_for_Fquality.Rmd.

```{r no_absvalue_analyses_sd}
#only for F=0.1 ###### start here
sd_stats <- sd_stats %>% filter(F_values==0.1) #%>% group_by(species) 
sd_stats$F_est_mean <- round(as.numeric(sd_stats$F_est), digits = 3)
sd_stats$k <- round(as.numeric(sd_stats$k), digits = 2)
sd_stats$M <- round(as.numeric(sd_stats$M), digits = 2)
sd_stats$k_M <- round(as.numeric(sd_stats$k_M), digits = 2)
sd_stats$Lfish_Lmat <- round(as.numeric(sd_stats$Lfish_Lmat), digits = 2)
sd_stats$Lfish_k <- round(as.numeric(sd_stats$Lfish_k), digits = 2)
sd_stats$Lfish_Linf <- round(as.numeric(sd_stats$Lfish_Linf), digits = 2)
sd_stats$AgeLfish_AgeHalfsat <- round(as.numeric(sd_stats$AgeLfish_AgeHalfsat), digits = 2)
#sd_stats$species <- as.factor(sd_stats$species)
# add theta calcuations for open population, R = 50 to the data frame after running theta_for_Fquality.Rmd
sd_stats <- left_join(sd_stats, openpop_theta, by = "species")
sd_stats$species  <- with(sd_stats, reorder(species, M))
sd_stats <- sd_stats %>% mutate(., theta_degrees = theta *(180/pi))
```
```{r no_absvalue_analyses_bias}
### For case when bias is not calculated as an absolute value
mean_stats_noabs <- filter(Fest_noabs, F_values==0.1) %>% group_by(species) 
mean_stats_noabs$F_est <- round(as.numeric(mean_stats_noabs$F_est), digits = 2)
mean_stats_noabs$k <- round(as.numeric(mean_stats_noabs$k), digits = 2)
mean_stats_noabs$M <- round(as.numeric(mean_stats_noabs$M), digits = 2)
mean_stats_noabs$k_M <- round(as.numeric(mean_stats_noabs$k_M), digits = 2)
mean_stats_noabs$Lfish_Lmat <- round(as.numeric(mean_stats_noabs$Lfish_Lmat), digits = 2)
mean_stats_noabs$Lfish_Linf <- round(as.numeric(mean_stats_noabs$Lfish_Linf), digits = 2)
mean_stats_noabs$Lfish_k <- round(as.numeric(mean_stats_noabs$Lfish_k), digits = 2)
mean_stats_noabs$AgeLfish_AgeHalfsat <- round(as.numeric(mean_stats_noabs$AgeLfish_AgeHalfsat), digits = 2)

# add theta calculations for open population, R = 50 to the data frame
mean_stats_noabs <- left_join(mean_stats_noabs, openpop_theta, by = "species")
mean_stats_noabs$species  <- with(mean_stats_noabs, reorder(species, M))
mean_stats_noabs <- mean_stats_noabs %>% mutate(., theta_degrees = theta *(180/pi))
```
ggplots of life history characteristics versus bias and standard deviation
```{r noabs_value_plots}
#k
Fest_noabs_kgg <- ggplot(data = mean_stats_noabs, aes(k_mean, F_est_mean))
Fest_noabs_kgg <- Fest_noabs_kgg + geom_point(aes(color = species), size = 4) + labs(x="k", y = "Bias") + geom_hline(aes(yintercept=0), linetype = "dashed") + geom_errorbar(aes(ymin=F_est_mean-F_est_sd, ymax=F_est_mean+F_est_sd), width=.02) 

#For only F=0.1
Fest_noabs_kgg_F01 <- ggplot(data = mean_stats_noabs, aes(k, F_est))
Fest_noabs_kgg_F01 <- Fest_noabs_kgg_F01 + geom_point(aes(color = species), size = 4) + labs(x="k", y = "Bias") + geom_hline(aes(yintercept=0), linetype = "dashed") 

Fest_std_kgg_F01 <- ggplot(data = sd_stats, aes(k, F_est))
Fest_std_kgg_F01 <- Fest_std_kgg_F01 + geom_point(aes(color = species), size = 4) + labs(x="k", y = "Standard error") + geom_hline(aes(yintercept=0), linetype = "dashed") 
## If want to have dots for F_est bias
#Combined for F=0.1
Fest_noabs_true_F01<- Fest_noabs_true %>% filter(F_values == "0.1")
Fest_noabs_true_F01 <- left_join(Fest_noabs_true_F01, openpop_theta, by = "species")
Fest_noabs_true_F01$species  <- with(Fest_noabs_true_F01, reorder(species, M))
Fest_noabs_true_Mgg_F01 <- ggplot(data = Fest_noabs_true_F01, aes(M, F_est))
Fest_noabs_true_Mgg_F01 <- Fest_noabs_true_Mgg_F01 + geom_point(aes(color = species), size = 4) + labs(x="Natural mortality", y = "F estimate") + geom_hline(aes(yintercept=0.1), linetype = "dashed") + geom_errorbar(aes(ymin=F_est-F_est_std, ymax=F_est+F_est_std), width=.02)  

#M
Fest_noabs_Mgg <- ggplot(data = mean_stats_noabs, aes(M, F_est))
Fest_noabs_Mgg <- Fest_noabs_Mgg + geom_point(aes(color = species), size = 4) + labs(x=expression(paste("Natural mortality rate (", y^-1, ")")), y = "Bias") + geom_hline(aes(yintercept=0), linetype = "dashed") + geom_errorbar(aes(ymin=F_est_mean-F_est_sd, ymax=F_est_mean+F_est_sd), width=.02) + theme(legend.title=element_blank())

#For only F=0.1
Fest_noabs_Mgg_F01 <- ggplot(data = mean_stats_noabs, aes(M, F_est, color = species))
Fest_noabs_Mgg_F01 <- Fest_noabs_Mgg_F01 + 
  geom_point(size = 4) + 
  geom_smooth(method = lm, color = "black") + 
  labs(x=expression(paste("Natural mortality rate (", y^-1, ")")), y = "Bias") + 
  geom_hline(aes(yintercept=0), linetype = "dashed") +
  theme(legend.title=element_blank()) +
  scale_color_manual(values = pal(17))

Fest_std_Mgg_F01 <- ggplot(data = sd_stats, aes(M, F_est, color = species))
Fest_std_Mgg_F01 <- Fest_std_Mgg_F01 + 
  geom_point(size = 4) +  
  geom_smooth(method = lm, color = "black") + 
  labs(x=expression(paste("Natural mortality rate (", y^-1, ")")), y = "Standard deviation") + 
  theme(legend.title=element_blank()) +
  scale_color_manual(values = pal(17))

Fest_noabs_Lgg <- ggplot(data = mean_stats_noabs, aes(Lfish_Linf, F_est))
Fest_noabs_Lgg <- Fest_noabs_Lgg + geom_point(aes(color = species), size = 4) + labs(x="Lfish_Linf", y = "Bias") + geom_hline(aes(yintercept=0), linetype = "dashed") + geom_errorbar(aes(ymin=F_est_mean-F_est_sd, ymax=F_est_mean+F_est_sd), width=.02) 

#For only F=0.1
Fest_noabs_Lgg_F01 <- ggplot(data = mean_stats_noabs, aes(Lfish_Linf, F_est))
Fest_noabs_Lgg_F01 <- Fest_noabs_Lgg_F01 + geom_point(aes(color = species), size = 4) + labs(x=expression(paste("Lfish/", "L"[inf])), y = "Bias") + geom_hline(aes(yintercept=0), linetype = "dashed") 

Fest_std_Lgg_F01 <- ggplot(data = sd_stats, aes(Lfish_Linf, F_est))
Fest_std_Lgg_F01 <- Fest_std_Lgg_F01 + geom_point(aes(color = species), size = 4) + labs(x="Lfish/Linf", y = "Standard deviation") + geom_hline(aes(yintercept=0), linetype = "dashed") 

Fest_noabs_k_Mgg <- ggplot(data = mean_stats_noabs, aes(k_M, F_est))
Fest_noabs_k_Mgg <- Fest_noabs_k_Mgg + geom_point(aes(color = species), size = 4) + labs(x="k/M", y = "Bias (not absolute)") + geom_hline(aes(yintercept=0), linetype = "dashed") + geom_errorbar(aes(ymin=F_est_mean-F_est_sd, ymax=F_est_mean+F_est_sd), width=.02) 

#For only F=0.1
Fest_noabs_k_Mgg_F01 <- ggplot(data = mean_stats_noabs, aes(k_M, F_est))
Fest_noabs_k_Mgg_F01 <- Fest_noabs_k_Mgg_F01 + geom_point(aes(color = species), size = 4) + geom_smooth(method = lm) + labs(x="k/M", y = "Bias") + geom_hline(aes(yintercept=0), linetype = "dashed") 

#linear regression equation
lm_eqn = function(m) {
  l <- list(a = format(coef(m)[1], digits = 2),
      b = format(abs(coef(m)[2]), digits = 2),
      r2 = format(summary(m)$r.squared, digits = 3));
  if (coef(m)[2] >= 0)  {
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2,l)
  } else {
    eq <- substitute(italic(y) == a - b %.% italic(x)*","~~italic(r)^2~"="~r2,l)    
  }
  as.character(as.expression(eq));                 
}

p1 = p + geom_text(aes(x = 25, y = 300, label = lm_eqn(lm(y ~ x, df))), parse = TRUE)

Fest_std_k_Mgg_F01 <- ggplot(data = sd_stats, aes(k_M, F_est))
Fest_std_k_Mgg_F01 <- Fest_std_k_Mgg_F01 + geom_point(aes(color = species), size = 4) + geom_smooth(method = lm) + labs(x="k/M", y = "Standard error") + geom_hline(aes(yintercept=0), linetype = "dashed") 

Fest_noabs_Lfish_Lmatgg <- ggplot(data = mean_stats_noabs, aes(Lfish_Lmat, F_est))
Fest_noabs_Lfish_Lmatgg <- Fest_noabs_Lfish_Lmatgg + 
  geom_point(aes(color = species), size = 4) + 
  labs(x="Lfish/Lmat", y = "Bias") + 
  geom_hline(aes(yintercept=0), linetype = "dashed") + 
  geom_smooth(method = lm, color = "black") + 
  geom_errorbar(aes(ymin=F_est_mean-F_est_sd, ymax=F_est_mean+F_est_sd), width=.02) + 
  theme(legend.title=element_blank())

#For only F=0.1 - bias and sd (df = sd_stats) 
Fest_noabs_Lfish_Lmatgg_F01 <- ggplot(data = mean_stats_noabs, aes(Lfish_Lmat, F_est))
Fest_noabs_Lfish_Lmatgg_F01 <- Fest_noabs_Lfish_Lmatgg_F01 + geom_point(aes(color = species), size = 4) + 
  geom_smooth(method = lm, color = "black") + 
  labs(x="Length at first harvest/length at maturity", y = "Bias") + 
  geom_hline(aes(yintercept=0), linetype = "dashed") 

Fest_sd_Lfish_Lmatgg_F01 <- ggplot(data = sd_stats, aes(Lfish_Lmat, F_est))
Fest_sd_Lfish_Lmatgg_F01 <- Fest_sd_Lfish_Lmatgg_F01 + geom_point(aes(color = species), size = 4) + labs(x="Length at first harvest/length at maturity", y = "Standard deviation") + geom_smooth(method = lm, color = "black") + geom_hline(aes(yintercept=0), linetype = "dashed") 

#Lfish/k - bias and sd for F=0.1 only
Fest_noabs_Lfish_k_F01 <- ggplot(data = mean_stats_noabs, aes(Lfish_k, F_est))
Fest_noabs_Lfish_k_F01 <- Fest_noabs_Lfish_k_F01 + geom_point(aes(color = species), size = 4) + labs(x="Lfish/k", y = "Bias (not absolute)") + geom_hline(aes(yintercept=0), linetype = "dashed") 

Fest_sd_Lfish_k_F01 <- ggplot(data = sd_stats, aes(Lfish_k, F_est))
Fest_sd_Lfish_k_F01 <- Fest_sd_Lfish_k_F01 + geom_point(aes(color = species), size = 4) + labs(x="Lfish/k", y = "Standard Error") + geom_hline(aes(yintercept=0), linetype = "dashed") 

#Age@enterfishery/Age@growthhalfsat - bias and sd for F=0.1 only
Fest_noabs_AgeLfish_AgeHalfsat_F01 <- ggplot(data = mean_stats_noabs, aes(AgeLfish_AgeHalfsat, F_est))
Fest_noabs_AgeLfish_AgeHalfsat_F01 <- Fest_noabs_AgeLfish_AgeHalfsat_F01 + geom_point(aes(color = species), size = 4) + labs(x="Age@Lfish/Age@Halfsat", y = "Bias (not absolute)") + geom_hline(aes(yintercept=0), linetype = "dashed") 

Fest_sd_AgeLfish_AgeHalfsat_F01 <- ggplot(data = sd_stats, aes(AgeLfish_AgeHalfsat_mean, F_est_mean))
Fest_sd_AgeLfish_AgeHalfsat_F01 <- Fest_sd_AgeLfish_AgeHalfsat_F01 + geom_point(aes(color = species), size = 4) + labs(x="Age@Lfish/Age@Halfsat", y = "Standard error") + geom_hline(aes(yintercept=0), linetype = "dashed") 
```
 theta for no absolute value vs. bias and standard deviation, F = 0.1
```{r theta}
theta_sd <- sd_stats %>% filter(!is.na(theta_degrees)) #%>% arrange(., M)
theta_sd$F_est_mean <- round(as.numeric(theta_sd$F_est), digits = 3)

theta_sd_gg <- ggplot(data = sd_stats, aes(theta_degrees, F_est_mean)) +
  geom_point(aes(color = species), size = 4) + 
  labs(x = expression(paste("Angle of deviation from ", italic(v["1"]), " (", theta, "," , ~degree, ")")), y = "Standard deviation") + 
  guides(colour = guide_legend(title = NULL)) + ylim(0, max(theta_sd$F_est_mean))

theta_bias <- mean_stats_noabs %>% filter(!is.na(theta_degrees))
theta_bias$F_est_mean <- round(as.numeric(theta_bias$F_est), digits = 2)

theta_bias_gg <- ggplot(data = theta_bias, aes(theta_degrees, F_est_mean)) +
  geom_point(aes(color = species), size = 4) + 
  labs(x = expression(paste("Angle of deviation from ", italic(v["1"]), " (", theta, "," , ~degree, ")")), y = "Bias") + 
  geom_hline(aes(yintercept=0), linetype = "dashed") 

theta <- plot_grid(theta_bias_gg + theme(legend.position = "none"), theta_sd_gg + 
    theme(legend.position = "none"), labels = c("a)", "b)"), align = 'vh',
           hjust = -1, nrow = 1) 

legend <- get_legend(theta_sd_gg) 
theta_legend <- plot_grid(theta + theme(plot.margin = unit(c(2,1,0,0), "cm")), legend, rel_widths = c(2, .4))

save_plot("Fest_theta_3Aug2018.pdf", theta_legend,
          ncol = 3, # we're saving a grid plot of 2 columns
          nrow = 1, # and 2 rows
          # each individual subplot should have an aspect ratio of 1.3
          base_aspect_ratio = 0.9
          )
```
###End of no absolute value analyses
```{r k_L_ratiokM}
mean_stats_kgg <- ggplot(data = mean_stats, aes(k_mean, F_est_mean))
mean_stats_kgg <- mean_stats_kgg + geom_point(aes(color = species), size = 4) + geom_errorbar(aes(ymin=F_est_mean-F_est_sd, ymax=F_est_mean+F_est_sd), width=.02) + labs(x="k", y = "Bias")

sd_stats_kgg <- ggplot(data = sd_stats, aes(k_mean, F_est_mean))
sd_stats_kgg <- sd_stats_kgg + geom_point(aes(color = species), size = 4) + labs(x="k", y = "Standard Error") 

mean_stats_Lgg <- ggplot(data = mean_stats, aes(Lfish_Linf_mean, F_est_mean))
mean_stats_Lgg <- mean_stats_Lgg + geom_point(aes(color = species), size = 4) + geom_errorbar(aes(ymin=F_est_mean-F_est_sd, ymax=F_est_mean+F_est_sd), width=.02) + labs(x="Lfish/Linf", y = "Bias")

sd_stats_Lgg <- ggplot(data = sd_stats, aes(Lfish_Linf_mean, F_est_mean))
sd_stats_Lgg <- sd_stats_Lgg + geom_point(aes(color = species), size = 4) + labs(x="Lfish/Linf", y = "Standard error") 

mean_stats_k_Mgg <- ggplot(data = mean_stats, aes(k_M_mean, F_est_mean))
mean_stats_k_Mgg <- mean_stats_k_Mgg + geom_point(aes(color = species), size = 4) + geom_errorbar(aes(ymin=F_est_mean-F_est_sd, ymax=F_est_mean+F_est_sd), width=.02) + labs(x="k/M", y = "Bias")

sd_stats_k_Mgg <- ggplot(data = sd_stats, aes(k_M_mean, F_est_mean))
sd_stats_k_Mgg <- sd_stats_k_Mgg + geom_point(aes(color = species), size = 4) + labs(x="k/M", y = "Standard error") # 

mean_stats_Mgg <- ggplot(data = mean_stats, aes(M_mean, F_est_mean))
mean_stats_Mgg <- mean_stats_Mgg + geom_point(aes(color = species), size = 4) + geom_errorbar(aes(ymin=F_est_mean-F_est_sd, ymax=F_est_mean+F_est_sd), width=.02) + labs(x="Natural mortality rate (M/yr)", y = "Bias")

sd_stats_Mgg <- ggplot(data = sd_stats, aes(M_mean, F_est_mean))
sd_stats_Mgg <- sd_stats_Mgg + geom_point(aes(color = species), size = 4) + labs(x="Natural mortality rate (M/yr)", y = "Standard error") 

mean_stats_maxagegg <- ggplot(data = mean_stats, aes(Max_age_mean, F_est_mean))
mean_stats_maxagegg <- mean_stats_maxagegg + geom_point(aes(color = species), size = 4) + geom_errorbar(aes(ymin=F_est_mean-F_est_sd, ymax=F_est_mean+F_est_sd), width=.02) + labs(x="Maximum age", y = "Bias")

sd_stats_maxagegg <- ggplot(data = sd_stats, aes(Max_age_mean, F_est_mean))
sd_stats_maxagegg <- sd_stats_maxagegg + geom_point(aes(color = species), size =4) + labs(x="Maximum age", y = "Standard error") 

#Combined for F=0.2 sample size (Fest_ss) and time series duration
Fest_ss1<- Fest_ss %>% filter(F_values == "0.2") 
Fest_ss1$F_est <- as.numeric(Fest_ss1$F_est)
Fest_ss1$F_est_std <- as.numeric(Fest_ss1$F_est_std)
ss <- ggplot(data = Fest_ss1, aes(sample_size, F_est, ymin = 0, ymax = 0.3))
ss <- ss + geom_point(aes(color = species), size = 4) + labs(x="Sample size", y = "Fishing mortality rate (F/yr)") + geom_hline(aes(yintercept=0.2), linetype = "dashed") + geom_errorbar(aes(ymin=F_est-F_est_std, ymax=F_est+F_est_std), width=.02) 

Fest_ts<- Fest_ss %>% filter(F_values == "0.1")
Fest_ts$F_est <- as.numeric(Fest_ts$F_est)
Fest_ts$F_est_std <- as.numeric(Fest_ts$F_est_std)

ts <- ggplot(data = Fest_ts, aes(duration, F_est, ymin = 0, ymax = 0.4))
ts <- ts + geom_point(aes(color = species), size = 4) + labs(x="Time series duration (yrs)", y = "Fishing mortality rate (F/yr)") + geom_hline(aes(yintercept=0.1), linetype = "dashed") + geom_errorbar(aes(ymin=F_est-F_est_std, ymax=F_est+F_est_std), width=.02)
```

```{r fig.width=8,fig.height=11}
#Plots
plot_grid(mean_stats_kgg, mean_stats_Lgg, mean_stats_Mgg, mean_stats_k_Mgg, labels = c("A", "B", "C", "D"), ncol = 2)
```
```{r fig.width=11,fig.height=8}
plot_grid(sd_stats_kgg, sd_stats_Lgg, sd_stats_Mgg, sd_stats_k_Mgg, labels = c("A", "B", "C", "D"), ncol = 2)
```
```{r fig.width=8,fig.height=11}
#No absolute value for bias
plot_grid(Fest_noabs_kgg, Fest_noabs_Lgg, Fest_noabs_Mgg, Fest_noabs_k_Mgg, labels = c("A", "B", "C", "D"), ncol = 2)
```
```{r fig.width=11,fig.height=8}
#No absolute value for bias F=0.1 only
plot_grid(Fest_noabs_kgg_F01, Fest_noabs_Lgg_F01, Fest_noabs_Mgg_F01, Fest_noabs_k_Mgg_F01, labels = c("A", "B", "C", "D"), ncol = 2)
```

```{r fig.width=11,fig.height=8}
plot_grid(Fest_std_kgg_F01, Fest_std_Lgg_F01, Fest_std_Mgg_F01, Fest_std_k_Mgg_F01, labels = c("A", "B", "C", "D"), ncol = 2)
```
```{r fig.width=11,fig.height=8}
colourCount = length(unique(sd_stats$species))
getPalette = colorRampPalette(brewer.pal(8, "RdBu"))

Fest_noabs_Lfish_Lmatgg_F01 <- ggplot(data = mean_stats_noabs, aes(Lfish_Lmat, F_est))
Fest_noabs_Lfish_Lmatgg_F01 <- Fest_noabs_Lfish_Lmatgg_F01 + geom_point(aes(color = species), size = 4) + 
  geom_smooth(method = lm, color = "black") + 
  labs(x="Length at first harvest/length at maturity", y = "Bias") + 
  geom_hline(aes(yintercept=0), linetype = "dashed") +
  scale_color_manual(values = getPalette(colourCount))

Fest_sd_Lfish_Lmatgg_F01 <- ggplot(data = sd_stats, aes(Lfish_Lmat, F_est))
Fest_sd_Lfish_Lmatgg_F01 <- Fest_sd_Lfish_Lmatgg_F01 + 
  geom_point(aes(color = species), size = 4) + 
  labs(x="Length at first harvest/length at maturity", y = "Standard deviation") + 
  geom_smooth(method = lm, color = "black") + 
  guides(colour = guide_legend(title = NULL)) + 
  scale_color_manual(values = getPalette(colourCount))

## color palette test ##

Lfish_Lmat_F01 <- plot_grid(Fest_noabs_Lfish_Lmatgg_F01 + theme(legend.position = "none"), Fest_sd_Lfish_Lmatgg_F01 + 
    theme(legend.position = "none"), labels = c("a)", "b)"), align = 'vh',
           hjust = -1, nrow = 1) 

legend_Lfish <- get_legend(Fest_sd_Lfish_Lmatgg_F01)#Fest_sd_Lfish_Lmatgg_F01
Lfish_Lmat_F01_legend <- plot_grid(Lfish_Lmat_F01 + theme(plot.margin = unit(c(2,1,0,0), "cm")), legend_Lfish, rel_widths = c(2, .4))

save_plot("Fest_Lfish_Lmat_F01_2Sep2018.pdf", Lfish_Lmat_F01_legend,
          ncol = 3, # we're saving a grid plot of 2 columns
          nrow = 1, # and 2 rows
          # each individual subplot should have an aspect ratio of 0.85
          base_aspect_ratio = 0.9
          ) 
```
```{r fig.width=11,fig.height=8}
Fest_noabs_Mgg_F01 <- ggplot(data = mean_stats_noabs, aes(M, F_est, color = species))
Fest_noabs_Mgg_F01 <- Fest_noabs_Mgg_F01 + 
  geom_point(size = 4) + 
  geom_smooth(method = lm, color = "black") + 
  labs(x=expression(paste("Natural mortality rate (", y^-1, ")")), y = "Bias") + 
  geom_hline(aes(yintercept=0), linetype = "dashed") +
  theme(legend.title=element_blank()) +
  scale_color_manual(values = pal(17))

Fest_std_Mgg_F01 <- ggplot(data = sd_stats, aes(M, F_est, color = species))
Fest_std_Mgg_F01 <- Fest_std_Mgg_F01 + 
  geom_point(size = 4) +  
  geom_smooth(method = lm, color = "black") + 
  labs(x=expression(paste("Natural mortality rate (", y^-1, ")")), y = "Standard deviation") + 
  theme(legend.title=element_blank()) +
  scale_color_manual(values = pal(17))

Mgg_F01 <- plot_grid(Fest_noabs_Mgg_F01 + theme(legend.position = "none"), Fest_std_Mgg_F01 + 
    theme(legend.position = "none"), labels = c("a)", "b)"), align = 'vh',
           hjust = -1, nrow = 1) 

legend_Mgg <- get_legend(Fest_std_Mgg_F01) 
Mgg_F01_legend <- plot_grid(Mgg_F01 + theme(plot.margin = unit(c(2,1,0,0), "cm")), legend_Mgg, rel_widths = c(2, .4))

save_plot("Fest_M_F01_1Sep2018.pdf", Mgg_F01_legend,
          ncol = 3, # we're saving a grid plot of 2 columns
          nrow = 1, # and 2 rows
          # each individual subplot should have an aspect ratio of 0.85
          base_aspect_ratio = 0.9
          )
```

```{r fig.width=8,fig.height=11}
plot_grid(Fest_noabs_AgeLfish_AgeHalfsat_F01, Fest_sd_AgeLfish_AgeHalfsat_F01, labels = c("A", "B"), ncol = 1)
#plot grid of what seem to be important predictors of bias and stddev using 
```