---
title: "openpop_metrics"
author: "Katie Kaplan"
date: "7/12/2018"
output: html_document
---
Edited by Lauren Yamane
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(data.table)
library(purrrlyr)
library(purrr)
```

## R Markdown
This is from Katie's MPApopulationmodels 1) openpop_time.R , 2) closedpop_metrics.R from: https://github.com/katherinekaplan/MPApopulationmodels/blob/master/R/
Removed parts of code from hers that were NA to open population case. 

```{r read_data}
RF_parms <- read.csv("/R_stuff/R_Research/MPAs/RFparmsforMEGAFUNCTION_LY.csv")
RF_parms2 <- RF_parms %>% select(-Species, -Lmat, -Fi.1) 

tf <- as.list(RF_parms2$tf)
maxage <- as.list(RF_parms2$maxage)
#Lmat <- as.list(RF_parms2$Lmat)
Lfish <- as.list(RF_parms2$Lfish)
M <- as.list(RF_parms2$M)
# Fi for fished pop before MPA is 0.1, Fi for unfished (post-MPA) pop is 0
Fi <- as.list(RF_parms2$Fi)
Linf <- as.list(RF_parms2$Linf)
k <- as.list(RF_parms2$k)
a0 <- as.list(RF_parms2$a0)
pW <- as.list(RF_parms2$pW)
qW <- as.list(RF_parms2$qW)
R <- as.list(RF_parms2$R)

parms_fished <- list(tf = tf, maxage = maxage, Lfish = Lfish, M = M, Fi = Fi, Linf = Linf, k = k, a0 = a0, pW = pW, qW = qW, R = R)
```
Also, refer to the 1979 Joel Cohen paper on the cumulative distance from an observed to a stable age structure (which describes how to calculate that value, D1 or D2, and the angle representing the similarity of initial conditions (fished state) to the unfished SAD (theta).
```{r openpop_time}
#1. Calculate the SADs of fished case and unfished case.  These will be used to calculate theta
openpop_time = function(tf, maxage, M, Fi, Lfish, Linf, k, a0, pW, qW, R) { 
  ##First step calculate the stable age distribution of the fished population
  a_harv0=(log((Lfish-Linf)/-Linf)/-k)+a0   ##age fished back calculated from von-B eqn
  agefish=round(a_harv0,digits=0) ##round age fished to integer
  N0=rep(100,maxage) #Initial pop vector, start with 100 individual in each age class
  N0[1]=R
  s=exp(-M)#no fishing case
  sf=exp(-(M+Fi)) ##fishing case
  sfx=rep(sf,maxage-1)
  sfx[1:(agefish-1)]=rep(s,(agefish-1))
  sxs=rep(s,maxage-1) #Survival vector ##number of s is ageclasses-1
  Nt = matrix(0,tf,maxage) #Initialize vector of population sizes with extra columns for spawners and recruitment before variability
  Nt[1,] = N0 #Put in initial values
  #set.seed(1) #Set the seed so that every simulation uses same random sequence
  t<-1
  ##Get deterministic equilibrium for fished state
  for(t in 1:(tf-1)) {
    Nt[t+1,1] = R#*(exp(sig_r*rnorm(1,mean=0, sd=1))) #Recruits after variability in column 1, rnorm to generate random number for 1 point (n=1)
    Nt[t+1,2:(maxage)] = sfx*Nt[t,1:(maxage-1)] #Survivorship of each age class  in columns 2-10
  }
  ##Second step use that stable age distribution of the fished population as the starting vector
  ##to determine the MPA effect
  N.fished=Nt[tf,]##the stable age dist values from the fished state
  return(N.fished)
}

# Determine the SAD for fished case, parms as named list
parms_fished$N.fished <- parms_fished %>%
  pmap(openpop_time)

# To find the SAD (w1) for the unfished case
Fi = rep(0,nrow(RF_parms2))
Fi = as.list(Fi)

parms_unfished <- list(tf = tf, maxage = maxage, Lfish = Lfish, M = M, Fi = Fi, Linf = Linf, k = k, a0 = a0, pW = pW, qW = qW, R = R)
# Change N.fished in openpop_time function to N.unfished and re-run the openpop_time function.  Then run the code here:
parms_unfished$N.unfished <- parms_unfished %>%
  pmap(openpop_time)

```
```{r openpop_metrics}
#2. Use fished and unfished SAD to calculate theta. 

fished_SAD <- parms_fished$N.fished
unfished_SAD <- parms_unfished$N.unfished

# Equation for theta: theta=acos((N0%*%w1)/(sqrt(sum(N0^2))*sqrt(sum(w1^2))))
theta_num <- map2(fished_SAD, unfished_SAD, `%*%`) 

theta_denom_fished <- map2(fished_SAD, fished_SAD, `*`) %>% map(., compose(sqrt, sum, unlist)) # for compose: applies functions from right to left (i.e., unlist, then sum, then sqrt)
theta_denom_unfished <- map2(unfished_SAD, unfished_SAD, `*`) %>% map(., compose(sqrt, sum, unlist)) 
theta_denom <- map2(theta_denom_fished, theta_denom_unfished, `*`)

theta <- map2(theta_num, theta_denom, `/`) %>% map(., acos)

#openpop_metrics(maxage=25,Lmat=18,Lfish=25,M=0.2,Fi=0.17, Linf=37.8,k=0.23,a0=-0.7,pW=6.29e-06,qW=3.172, N.fished = parms$N.fished[[1]]) 

species <- as.data.frame(RF_parms$Species)
theta_dbl <- flatten_dbl(theta)
openpop_theta <- bind_cols(species = species, theta = theta_dbl)
names(openpop_theta)[1] <- c("species")

### Now use openpop_theta in Fquality.Rmd ####
```

